SignalHsmm - a novel semi-Markov model of eukaryotic signal peptides

### 2015-06-20 paper.tex
caption improved

\begin{figure}[ht]\centering
\includegraphics[width=0.95\textwidth]{figures/enccomp.eps}
\caption{Comparison of amino acid encodings with the best sensitivity and the best
specificity in different regions of signal peptide and mature proteins according to: A) the normalized value of
property; points represent amino acids; B) frequencies of amino acids in the given region.}
\label{fig:enccomp}
\end{figure}

>>>>

\begin{figure}[ht]\centering
\includegraphics[width=0.95\textwidth]{figures/enccomp.eps}
\caption{Comparison of amino acid encodings with the best sensitivity and the best
specificity in different regions of signal peptide and mature proteins according to: A) the normalized value of
properties for particular amino acids (points) and B) frequencies of amino acids in the given region.}
\label{fig:enccomp}
\end{figure}
